Example Manuscript Template for a Data Analysis Project

### 2024-03-17 products/manuscript/workspace.qmd
Still getting data and graphs under control
Still getting data and graphs under control

```{r}
#Call a bunch of libraries.
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(broom)) 
suppressPackageStartupMessages(library(here))
suppressPackageStartupMessages(library(readxl)) 
suppressPackageStartupMessages(library(dplyr)) 
suppressPackageStartupMessages(library(tidyr)) 
suppressPackageStartupMessages(library(skimr))
suppressPackageStartupMessages(library(gt))
suppressPackageStartupMessages(library(dslabs))
suppressPackageStartupMessages(library(plotly))
suppressPackageStartupMessages(library(gapminder))
suppressPackageStartupMessages(library(kableExtra))

@@

@@

WHO_data_fluB <- WHO_data_flu %>% filter(WHOREGION == "AFR") %>% mutate (INF_AFR = INF_ALL)
WHO_data_fluB <- WHO_data_flu %>% filter(WHOREGION == "AMR") %>% mutate (INF_AMR = INF_ALL)
WHO_data_fluB <- WHO_data_flu %>% filter(WHOREGION == "EUR") %>% mutate (INF_EUR = INF_ALL)
WHO_data_fluB <- WHO_data_flu %>% filter(WHOREGION == "WPR") %>% mutate (INF_WPR = INF_ALL)

plot2A <- ggplot(WHO_data_fluB, aes(x = MMWR_WEEKSTARTDATE)) +
  geom_point(aes(y = INF_AFR), color = "red") +
  geom_line(aes(y = INF_AFR), color = "red") +
  geom_point(aes(y = INF_AMR), color = "blue") +
  geom_line(aes(y = INF_AMR), color = "blue") +
  geom_point(aes(y = INF_EUR), color = "green") +
  geom_line(aes(y = INF_EUR), color = "green") +
  geom_point(aes(y = INF_WPR), color = "magenta") +
  geom_line(aes(y = INF_WPR), color = "magenta") +
  labs(x = "DATE", y = "Total Reported Cases of FLU", title = "Scatterplot Flu Cases Per WHO Region for the 2023-2024 Flu Season") +
  theme_minimal()

plot2Asave = here("assets", "plot2A.png")
ggsave(plot2Asave, plot2A, width = 10, height = 6, dpi = 300)

#| label: fig-schematic
#| fig-cap: "Figure 6: World Flu Burden by Region Over the 2023-2024 Flu Season."
#| echo: FALSE
knitr::include_graphics(here("assets","plot2A.png"))

>>>>

```{r}
#Call a bunch of libraries.
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(broom)) 
suppressPackageStartupMessages(library(here))
suppressPackageStartupMessages(library(readxl)) 
suppressPackageStartupMessages(library(dplyr)) 
suppressPackageStartupMessages(library(tidyr)) 
suppressPackageStartupMessages(library(skimr))
suppressPackageStartupMessages(library(gt))
suppressPackageStartupMessages(library(dslabs))
suppressPackageStartupMessages(library(plotly))
suppressPackageStartupMessages(library(gapminder))
suppressPackageStartupMessages(library(kableExtra))
suppressPackageStartupMessages(library(openxlsx))
suppressPackageStartupMessages(library(xlsx))

@@

print(summarized_data)

write.csv(summarized_data, file = "summarized_data.csv", row.names = FALSE)

@@

summarized_dataB <- WHO_data_fluB %>%
  group_by(WHOREGION, MMWR_WEEKSTARTDATE) %>%
  summarize(TOT_INF_A = sum(INF_A))

print(summarized_dataB)

write.csv(summarized_data, file = "summarized_dataB.csv", row.names = FALSE)

summarized_dataC <- WHO_data_fluB %>%
  group_by(WHOREGION, MMWR_WEEKSTARTDATE) %>%
  summarize(TOT_INF_B = sum(INF_B))

print(summarized_dataC)

write.csv(summarized_data, file = "summarized_dataC.csv", row.names = FALSE)

selected_regions1 <- c("WPR", "AMR", "EUR")
selected_regions2 <- c("AFR", "SEAR", "EMR")

# Filter the dataset for the selected regions
subset_data1 <- subset(summarized_data, WHOREGION %in% selected_regions1)
subset_data2 <- subset(summarized_data, WHOREGION %in% selected_regions2)

plot2D <- ggplot(subset_data1, aes(x=MMWR_WEEKSTARTDATE)) +
  geom_point(aes(y=TOT_INF_ALL, color = WHOREGION)) +
  geom_line(aes(y=TOT_INF_ALL, color = WHOREGION)) +
    labs(x = "DATE", y = "Total Reported Cases of FLU", title = "Scatterplot Flu Cases Per WHO Region for the 2023-2024 Flu Season") +
  theme_minimal()

plot2Dsave = here("assets", "plot2D.png")
ggsave(plot2Dsave, plot2D, width = 10, height = 6, dpi = 300)

#| label: fig-schematic
#| fig-cap: "Figure 8: World Flu Burden by Region Over the 2023-2024 Flu Season."
#| echo: FALSE
knitr::include_graphics(here("assets","plot2D.png"))

plot2E <- ggplot(subset_data2, aes(x=MMWR_WEEKSTARTDATE)) +
  geom_point(aes(y=TOT_INF_ALL, color = WHOREGION)) +
  geom_line(aes(y=TOT_INF_ALL, color = WHOREGION)) +
    labs(x = "DATE", y = "Total Reported Cases of FLU", title = "Scatterplot Flu Cases Per WHO Region for the 2023-2024 Flu Season") +
  theme_minimal()

plot2Esave = here("assets", "plot2E.png")
ggsave(plot2Esave, plot2E, width = 10, height = 6, dpi = 300)

#| label: fig-schematic
#| fig-cap: "Figure 9: World Flu Burden by Region Over the 2023-2024 Flu Season."
#| echo: FALSE
knitr::include_graphics(here("assets","plot2E.png"))
